---
title: "Saints Fan Persona Analysis"
subtitle: "Neighborhood Intelligence & Sponsorship Alignment"
author: "Nathan Vernon"
format: 
  html:
    theme: flatly
    mainfont: "Century Gothic"
    toc: true
    code-fold: true
    echo: false
    self-contained: true
    grid:
      body-width: 1200px
---

# **Executive Summary**

This analysis identifies the demographic and economic drivers of Saints fan loyalty. By merging primary survey data with U.S. Census Bureau American Community Survey (ACS) metrics, we can get a more holistic view of This report specifically examines how neighborhood-level wealth and age correlate with fan passion and brand recall.

```{r}
#| label: data-engineering
#| message: false

# Load in all necessary libraries and fonts
windowsFonts(`Century Gothic` = windowsFont("Century Gothic"))
library(tidyverse)



# Load the joined data
df <- read_csv("data/saints_with_census.csv")

# We calculate the row-wise mean of the four passion variables
df_cleaned <- df %>%
  mutate(Passion_Score = (p1 + p2 + p3 + p4) / 4) %>%
  # Filter out any respondents who didn't answer these questions
  filter(!is.na(Passion_Score))

# Quick check to see the first 5 rows of our new metric
head(df_cleaned %>% select(p1, p2, p3, p4, Passion_Score))
```

## Exploratory Data Analysis

Exploratory data analysis began with the production of univariate plots to provide an initial understanding of the fanbase.

### Response Variable: Fan Passion

The primary response variable of interest is overall Fan Passion. Because passion is multifaceted, this metric was calculated as an aggregated index (0-100) using four distinct survey questions regarding fan loyalty and engagement.

As illustrated in Figure 1, the distribution of passion values follows a left-skewed pattern. Most observations fall around 95, indicating that the Saints fan base in this sample are very passionate.

```{r}
#| label: response-variable-eda
#| fig-cap: "Figure 1: Distribution of Calculated Fan Passion Scores"

ggplot(df_cleaned, aes(x = Passion_Score)) +
  geom_density(fill = "#C2B067", color = "black", alpha = 0.6) + # Saints Gold
  labs(
    title = "Response Variable: Fan Passion",
    subtitle = "Aggregated index calculated from survey variables P1-P4",
    x = "Passion Score (0-100)",
    y = "Density",
  ) +
  theme_minimal(base_family = "Century Gothic") +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_blank()
  
  )
```

### Predictor: Neighborhood Economics

To understand the geographic context of the fanbase, we analyzed the relationship between a fan's stated passion and the median household income of their ZIP Code Tabulation Area (ZCTA) using U.S. Census Bureau ACS data.

When compared with overall passion, the neighborhood income variable demonstrates a statistically flat relationship with a slight negative trend (Figure 2). This suggests that Saints fan passion transcends economic boundaries, and that the most deeply engaged fans are slightly more concentrated in middle-to-lower-income neighborhoods.

```{r}
#| label: income-passion-bivariate
#| fig-cap: "Figure 2: Relationship between Neighborhood Income and Fan Passion"
#| echo: false
#| message: false
#| warning: false

# 1. Calculate the correlation (r) dynamically, ignoring NAs
correlation <- cor(df_cleaned$neighborhood_income, df_cleaned$Passion_Score, use = "complete.obs")
# Create a clean text label for the plot
cor_label <- paste0("Correlation (r) = ", round(correlation, 3))

# 2. Build the plot (filtering out the Census NAs so you don't get warnings)
ggplot(df_cleaned |>  filter(!is.na(neighborhood_income)), aes(x = neighborhood_income, y = Passion_Score)) +
  geom_jitter(color = "black", alpha = 0.3, size = 1.5) +
  geom_smooth(method = "lm", color = "#C2B067", linewidth = 1.5, se = TRUE) +
  scale_x_continuous(labels = scales::dollar_format()) +
  labs(
    title = "Neighborhood Wealth vs. Fan Passion",
    caption = cor_label, # This prints your exact stat in the bottom corner!
    x = "Median Neighborhood Income (ZCTA)",
    y = "Passion Score (0-100)"
  ) +
  theme_minimal(base_family = "Century Gothic") +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    panel.grid.minor = element_blank()
  )
```

### Predictor (Categorical): Season Ticket Holder Status

For categorical predictors, distinct group-level patterns are often evaluated to understand the baseline passion required to convert a casual follower into a dedicated ticket product investor.

However, when segmenting the Saints fan base by Season Ticket Holder (STH) status, the data reveals that average passion scores are nearly identical across both groups (Figure 3).

This indicates a highly ubiquitous and deeply entrenched fan base. Unlike markets where passion is heavily concentrated among in-stadium attendees, Saints fan affinity remains exceptionally high regardless of financial investment in tickets. For brand partners, this means sponsorship assets outside the stadium (e.g., broadcast, digital, and retail activations) carry just as much weight and reach a highly devoted audience.

```{r}
#| label: sth-categorical-plot
#| fig-cap: "Figure 3: Average Fan Passion by Season Ticket Holder Status"
#| echo: false
#| message: false
#| warning: false

# 1. Prepare the data: Calculate averages and create Ian's "(n = X)" labels
sth_summary <- df_cleaned |> 
  # Filter out missing STH data if any
  filter(!is.na(sth)) |> 
  # Convert 1/0 to readable labels 
  mutate(sth_label = ifelse(sth == 1, "Season Ticket Holder", "Non-Ticket Holder")) |> 
  group_by(sth_label) |> 
  summarise(
    avg_passion = mean(Passion_Score, na.rm = TRUE),
    n_fans = n()
  ) |> 
  # Create the Wakefield-style label: "85.2 (n = 450)"
  mutate(bar_label = paste0(round(avg_passion, 1), " (n = ", n_fans, ")"))

# 2. Build the horizontal bar chart
ggplot(sth_summary, aes(x = avg_passion, y = reorder(sth_label, avg_passion))) +
  # Ian uses a dark gray for these categorical bars
  geom_col(fill = "#C2B067", width = 0.5) + 
  # Add the labels right outside the bars
  geom_text(aes(label = bar_label), hjust = -0.2, family = "Century Gothic", size = 4) +
  # Extend the x-axis slightly so the text doesn't get cut off
  scale_x_continuous(limits = c(0, 110), breaks = seq(0, 100, 25)) +
  labs(
    title = "Impact of Ticket Status on Passion",
    x = "Average Passion Score",
    y = NULL # Hiding the Y-axis title to keep it clean like Ian's
  ) +
  theme_minimal(base_family = "Century Gothic") +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(), # Removes horizontal lines behind the bars
    axis.text.y = element_text(face = "bold", size = 11)
  )
```

### Predictor: In-Venue Attendance

While baseline passion remains high across the overall fanbase, we also evaluated the impact of physical, in-venue engagement. By analyzing the total number of home games a fan attended during the season (`attend`), we can determine if repeated physical exposure to the team and its sponsors correlates with heightened team affinity.

```{r}
#| label: attendance-progression-plot
#| fig-cap: "Figure 4: Average Fan Passion by Exact Number of Games Attended"
#| echo: false
#| message: false

# 1. Prepare the data: Group by exact number, cap at 8+
attend_summary <- df_cleaned |> 
  filter(!is.na(attend)) |> 
  # If attendance is 8 or more, make it "8+", otherwise keep the number
  mutate(attend_grouped = ifelse(attend >= 8, "8+", as.character(attend))) |> 
  # Lock the order from 0 to 8+ so the chart flows correctly left-to-right
  mutate(attend_grouped = factor(attend_grouped, levels = c("0", "1", "2", "3", "4", "5", "6", "7", "8+"))) |> 
  group_by(attend_grouped) |> 
  summarise(
    avg_passion = mean(Passion_Score, na.rm = TRUE),
    n_fans = n()
  ) |> 
  # Create the Wakefield-style label (using \n to put the 'n' on a new line)
  mutate(bar_label = paste0(round(avg_passion, 1), "\n(n=", n_fans, ")"))

# 2. Build the vertical column chart
ggplot(attend_summary, aes(x = attend_grouped, y = avg_passion)) +
  # Ian's categorical dark gray
  geom_col(fill = "#C2B067", width = 0.7) + 
  # Add the labels right on top of the bars
  geom_text(aes(label = bar_label), vjust = -0.2, family = "Century Gothic", size = 3.5) +
  # Extend the y-axis so the text doesn't get cut off
  scale_y_continuous(limits = c(0, 115), breaks = seq(0, 100, 25)) +
  labs(
    title = "Passion Progression by Games Attended",
    x = "Number of Home Games Attended",
    y = "Average Passion Score"
  ) +
  theme_minimal(base_family = "Century Gothic") +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(), # Removes vertical lines behind the bars
    axis.text.x = element_text(face = "bold", size = 11)
  )
```

### Predictor: Neighborhood Family Density

To further define the demographic profile of the fanbase, I analyzed life-stage indicators using U.S. Census Bureau ACS data. By calculating the percentage of households with children under 18 in each respondent's neighborhood, I tested if family-dense environments act as an incubator for team passion.

```{r}
#| label: family-density-plot
#| fig-cap: "Figure 5: Relationship between Neighborhood Family Density and Fan Passion"
#| echo: false
#| message: false
#| warning: false

# 1. Calculate the correlation (r)
cor_kids <- cor(df_cleaned$pct_kids, df_cleaned$Passion_Score, use = "complete.obs")
cor_label_kids <- paste0("Correlation (r) = ", round(cor_kids, 3))

# 2. Build the visual
ggplot(df_cleaned |> filter(!is.na(pct_kids)), aes(x = pct_kids, y = Passion_Score)) +
  geom_jitter(color = "black", alpha = 0.3, size = 1.5) +
  geom_smooth(method = "lm", color = "#C2B067", linewidth = 1.5, se = TRUE) +
  # Format the X-axis as clean percentages (e.g., 25%, 50%)
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    title = "Neighborhood Family Density vs. Fan Passion",
    caption = cor_label_kids,
    x = "Households with Children Under 18 (%)",
    y = "Passion Score (0-100)"
  ) +
  theme_minimal(base_family = "Century Gothic") +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    panel.grid.minor = element_blank()
  )
```

### Predictor: Neighborhood Education Level

To evaluate the impact of educational attainment, I analyzed the relationship between fan passion and the percentage of adults (age 25+) holding a Bachelor's degree or higher in the respondent's ZIP code.

```{r}
#| label: education-scatter-plot
#| fig-cap: "Figure 6: Relationship between Neighborhood Education and Fan Passion"
#| echo: false
#| message: false
#| warning: false

# 1. Calculate the correlation (r)
cor_edu <- cor(df_cleaned$pct_college, df_cleaned$Passion_Score, use = "complete.obs")
cor_label_edu <- paste0("Correlation (r) = ", round(cor_edu, 3))

# 2. Build the visual
ggplot(df_cleaned %>% filter(!is.na(pct_college)), aes(x = pct_college, y = Passion_Score)) +
  geom_jitter(color = "black", alpha = 0.3, size = 1.5) +
  geom_smooth(method = "lm", color = "#C2B067", linewidth = 1.5, se = TRUE) +
  # Format the X-axis as clean percentages
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    title = "Neighborhood Education Level vs. Fan Passion",
    caption = cor_label_edu,
    x = "Adults (25+) with a College Degree (%)",
    y = "Passion Score (0-100)"
  ) +
  theme_minimal(base_family = "Century Gothic") +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    panel.grid.minor = element_blank()
  )
```

#### Predictor: Neighborhood Education Tiers (ANOVA)

While a continuous correlation provides directional insight, we applied an Analysis of Variance (ANOVA) to definitively test for statistical significance. We segmented the respondent ZIP codes into three equal tiers (tertiles) based on the density of college-educated adults to determine if neighborhood education level creates a proven variance in fan passion.

```{r}
#| label: education-anova-plot
#| fig-cap: "Figure 7: Average Fan Passion by Neighborhood Education Tiers"
#| echo: false
#| message: false
#| warning: false

# 1. Prepare the Data: Create 3 equal buckets (Tertiles) for the ANOVA
df_edu <- df_cleaned |> 
  filter(!is.na(pct_college)) |> 
  mutate(
    # ntile() ranks the neighborhoods and splits them into 3 even groups
    edu_tier = ntile(pct_college, 3),
    edu_label = case_when(
      edu_tier == 1 ~ "Low Degree Density",
      edu_tier == 2 ~ "Moderate Degree Density",
      edu_tier == 3 ~ "High Degree Density"
    ),
    # Lock the order so the chart flows naturally left-to-right
    edu_label = factor(edu_label, levels = c("Low Degree Density", "Moderate Degree Density", "High Degree Density"))
  )

# 2. Run the ANOVA Model
anova_model <- aov(Passion_Score ~ edu_label, data = df_edu)
anova_summary <- summary(anova_model)

# 3. Extract the p-value to dynamically print on the chart
p_val <- anova_summary[[1]][["Pr(>F)"]][1]

# Create a clean label for the client
p_label <- ifelse(p_val < 0.05, 
                  paste0("ANOVA: Significant Variance (p = ", signif(p_val, 3), ")"), 
                  paste0("ANOVA: No Significant Variance (p = ", signif(p_val, 3), ")"))

# 4. Summarize for the Bar Chart
edu_summary <- df_edu |> 
  group_by(edu_label) |> 
  summarise(
    avg_passion = mean(Passion_Score, na.rm = TRUE),
    n_fans = n()
  ) |> 
  mutate(bar_label = paste0(round(avg_passion, 1), "\n(n=", n_fans, ")"))

# 5. Build the Visual
ggplot(edu_summary, aes(x = edu_label, y = avg_passion)) +
  geom_col(fill = "#C2B067", width = 0.6) + 
  geom_text(aes(label = bar_label), vjust = -0.2, family = "Century Gothic", size = 4) +
  scale_y_continuous(limits = c(0, 115), breaks = seq(0, 100, 25)) +
  labs(
    title = "Fan Passion by Neighborhood Education Tiers",
    caption = p_label, # This prints your exact ANOVA result in the corner!
    x = NULL,
    y = "Average Passion Score"
  ) +
  theme_minimal(base_family = "Century Gothic") +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.text.x = element_text(face = "bold", size = 11)
  )
```

## Conclusion: Variable Importance Modeling

While individual predictors provide excellent directional insight, audience demographics do not exist in a vacuum. To determine the true, independent drivers of fan affinity, we constructed a Multivariate Linear Regression model combining all major categorical and continuous variables.

By extracting the absolute t-statistics from the model, we can rank the relative "importance" of each variable in predicting a fan's Passion Score.

```{r}
#| label: regression-table
#| tbl-cap: "Table 1: Multivariate Linear Regression Output"
#| echo: false
#| message: false
#| warning: false

library(broom)
library(gt)

# 1. Build the Multivariate Linear Regression Model
final_model <- lm(Passion_Score ~ neighborhood_income + pct_college + pct_kids + sth + attend, data = df_cleaned)

# 2. Tidy the results and build the wide gt table
tidy(final_model) |> 
  mutate(term = case_when(
    term == "(Intercept)" ~ "Baseline Passion (Intercept)",
    term == "neighborhood_income" ~ "Neighborhood Income",
    term == "pct_college" ~ "Education Level (% College)",
    term == "pct_kids" ~ "Family Density (% Kids)",
    term == "sth" ~ "Season Ticket Holder",
    term == "attend" ~ "Games Attended",
    TRUE ~ term
  )) |> 
  # Keep the t-statistic column this time instead of making it a chart
  select(term, estimate, std.error, statistic, p.value) |> 
  gt() |> 
  tab_header(
    title = md("**Predictors of Fan Passion**"),
    subtitle = "Multivariate Linear Regression Results"
  ) |> 
  fmt_number(
    columns = c(estimate, std.error, statistic),
    decimals = 3
  ) |> 
  fmt_number(
    columns = p.value,
    decimals = 3
  ) |> 
  cols_label(
    term = "Predictor Variable",
    estimate = "Estimate (Coefficient)",
    std.error = "Standard Error",
    statistic = "t-Statistic",
    p.value = "P-Value"
  ) |> 
  tab_options(
    table.width = pct(100), # Forces the table to stretch wide
    table.font.names = "Century Gothic",
    heading.align = "left",
    table.border.top.color = "#C2B067", 
    table.border.top.width = px(3),
    column_labels.font.weight = "bold"
  )
```

### Relative Variable Importance

To make these findings highly actionable, we extracted the absolute t-statistics from the model to rank the relative "importance" of each variable. This allows us to see exactly which demographic or behavioral factor is the strongest independent driver of fan passion.

```{r}
#| label: importance-chart
#| fig-cap: "Figure 8: Relative Importance of Predictors on Fan Passion"
#| echo: false
#| message: false
#| warning: false

# 1. Extract the data for the chart (excluding the Intercept)
model_results <- tidy(final_model) |> filter(term != "(Intercept)")

# 2. Clean the names and grab the absolute t-statistic
importance_df <- model_results |>
  mutate(
    Importance = abs(statistic),
    Clean_Term = case_when(
      term == "neighborhood_income" ~ "Neighborhood Income",
      term == "pct_college" ~ "Education Level",
      term == "pct_kids" ~ "Family Density",
      term == "sth" ~ "STH Status",
      term == "attend" ~ "Games Attended",
      TRUE ~ term
    )
  )

# 3. Build the standalone horizontal bar chart
ggplot(importance_df, aes(x = Importance, y = reorder(Clean_Term, Importance))) +
  geom_col(fill = "#C2B067", width = 0.6) + 
  geom_text(aes(label = round(Importance, 2)), hjust = -0.2, family = "Century Gothic", size = 4) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.15))) + 
  labs(
    title = "What Actually Drives Fan Passion?",
    subtitle = "Relative Variable Importance (Absolute t-statistics)",
    x = "Relative Importance (Statistical Weight)",
    y = NULL
  ) +
  theme_minimal(base_family = "Century Gothic") +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 12, color = "gray40"),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(face = "bold", size = 12)
  )
```
